\documentclass[11pt]{book}
%\usepackage{utf8}{inputenc} % For Norwegian characters.
\usepackage{geometry}        
\geometry{letterpaper}    
\usepackage[parfill]{parskip}  
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{tabularx}
\usepackage{minitoc}
\usepackage{wrapfig}
\usepackage{pdfpages}
\usepackage{longtable}
\usepackage{subfig}
\usepackage{makeidx}
\usepackage{fancyhdr}

\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\usepackage[colorlinks=true, pdfstartview=FitV, linkcolor=blue, 
            citecolor=blue, urlcolor=blue]{hyperref}
            
\usepackage[T1]{fontenc}
\usepackage[ansinew]{inputenc}
\usepackage[english]{babel}
\usepackage{csquotes}
\usepackage[subsection,toc3]{javadoc}


%\pagestyle{fancy}

\pagestyle{fancyplain}
\setlength{\headheight}{15pt} 
\fancyhf{} 
\lhead{\fancyplain{}{\footnotesize\leftmark}}
%\chead{\fancyplain{}{\footnotesize\chaptername}}
\rhead{\fancyplain{}{\footnotesize\rightmark}}

%\lfoot{\fancyplain{}{\footnotesize\thechapter}}
\cfoot{\fancyplain{}{\footnotesize\thepage}}
%\rfoot{\fancyplain{}{\footnotesize\thesection}}

\newtheorem{theorem}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}{Definition}
\newtheorem{lemma}{Lemma}
\newtheorem{exercise}{Exercise}
\newtheorem{remark}{Remark}
\newtheorem{example}{Example}
\newtheorem{warning}{Warning}

\def\grad{ \mbox{grad}}
\def\curl{ \mbox{curl}}
\def\div{ \mbox{div}}
\def\U{\ensuremath {\cal U}}
\def\S{\ensuremath {\cal S}}
\def\V{\ensuremath {\cal V}}
\def\R{\ensuremath {\cal R}}
\def\tr{\ensuremath {\mbox{tr}}}

% ------------------- Title and Author -----------------------------
\title{Project Report\\
TDT4290 - Customer Driven Project \\ 
"Privacy Advisor"}

\author{GROUP 4\\
Ulf Nore, Nicholas Gerstle, Henrik Knutsen, Dimitry Kongevold,\\ 
Einar Afiouni, Neshahavan Karunakaran, Amanpreet Kaur}

\date{NTNU, Fall 2011}


\makeindex
\begin{document}

\dominitoc 

\frontmatter
\maketitle

\chapter*{\centering Abstract}
%background
This report details the design, development and implementation of the
"Privacy Advisor" software in fulfillment of course TDT4290-Customer
Driven Project. Privacy Advisor is developed as part of a larger project for SINTEF ICT, in
order to investigate the applicability of machine learning to aid users in
making internet privacy decisions. 

% method
Previous research at SINTEF has pointed
out several advantages of using a Case Based Reasoning (CBR) agent as
a promising machine learning technique in the field of privacy advice,
which is also what the Privacy Advisor is based on. SINTEF ICT
has indicated the use of the project software as part of future
research and therefore emphasis is placed on implementing a broad
and modular testing framework, rather than actual algorithms.

% result
The resulting product is a Java based framework with a central CBR
engine that is extendable with respect to key algorithms, databases
and user interfaces. It allows for network communication with a
community server that could implement a collaborative filtering approach 
similar to the CBR.

% conclusion
Privacy Advisor is aimed towards future research in privacy
enhancement techonology and is therefore build as a testing
framework. The core engine however, is flexible enough to be expanded
on for future development.



%more details in results?

%\dominitoc

\listoftables

\listoffigures

\tableofcontents \label{toc}

\pagenumbering{arabic}


\chapter{Introduction}

This report describes the development of a machine learning systems for aiding users in Internet privacy decisions. The software is titled "Privacy Advisor" and uses a case based reasoning (CBR) approach, which is a learning method that seeks to predict preferences based on previous user choices. The project is part of the course TDT4290 - Customer Driven Project and is part of a SINTEF ICT research project in privacy agents. The report is written in a chronological order where each chapter represents a distinct "phase" in the development process. In reality, of course, there are no crisp boundaries, but the structure here provides a useful structure for reasoning about the process. 

The structure of the report is as follows. Part~\ref{p1} describes the initial phase of the project; the projects directive, the planning phase, and the preliminary study phase. The project directive gives a high level overview over the project, its objectives, how they are reached, project scope, resources available etc. The preliminary study comprises the first weeks of the project, and is a consistent effort to better grasp the problem at hand, identify how it can be broken into subproblems and what tools are required to solve these problems. It also seeks to identify to some extent what the priorities of the project are; that is, given scarce resources, which objectives are prioritized. The project planning phase seeks to make more fine grained decisions on how resources are best allocated over time and to the various tasks that comprise the project.

Part~\ref{p2} describes the requirements specification, the design phase, implementation and documentation. The requirements specification is a contract between the customer and the project team where the the requirements to be satisfied by the software are stated explicitly. Based on the requirements, a design is made, which henceforth serves as a guideline for implementing the software system.

% TODO
Finally, Part~\ref{p3} describes the software testing stage. It also
contains a chapter evaluating the project as a whole and a summary of
the project work. It also looks at future extensions and some
challenges that need to be addressed in future development.

\part{Initial Phase - Planning and Research}\label{p1}
\addtocounter{chapter}{1}
\setcounter{section}{0}
\include{ProjectDirective/ProjectDirective}

\setcounter{section}{0}
\addtocounter{chapter}{1}
\include{PrelimStudy/PrelimReport}

\setcounter{section}{0}
\addtocounter{chapter}{1}
\include{PlanReport/PlanReport}

\part{Design and Implementation Phase}\label{p2}
\setcounter{section}{0}
\addtocounter{chapter}{1}
\include{ReqSpec/ReqSpec}

\setcounter{section}{0}
\addtocounter{chapter}{1}
\include{DesignReport/DesignReport}

\setcounter{section}{0}
\addtocounter{chapter}{1}
\include{Implementation/ImplementationReport}

\part{Testing, Evaluation and Summary}\label{p3}

\setcounter{section}{0}
\addtocounter{chapter}{1}
\include{Testing/TestPlan}

\setcounter{section}{0}
\addtocounter{chapter}{1}
\include{Evaluation/Evaluation}

\setcounter{section}{0}
\addtocounter{chapter}{1}
\include{Conclusion/Conclusion}

% Appendices
\part{Appendices}
\appendix
\Alph{chapter}
\setcounter{chapter}{1}
\include{Documentation/DocumentationReport}

\include{Appendix/RiskTables}
\include{Appendix/TestCases}
\include{Appendix/TestExecution}
\include{Appendix/Templates}

\makeatletter\@openrightfalse
\chapter{Javadoc}

\section{Main}
\include{Appendix/javadoc/com.kpro.mainGio}
\include{Appendix/javadoc/com.kpro.mainPrivacyAdviser}

\section{Algorithm}
\include{Appendix/javadoc/com.kpro.algorithmCBR}
\include{Appendix/javadoc/com.kpro.algorithmReductionAlgorithm}
\include{Appendix/javadoc/com.kpro.algorithmReduction-KNN}
\include{Appendix/javadoc/com.kpro.algorithmDistanceMetric}
\include{Appendix/javadoc/com.kpro.algorithmBitmapwithdata}
\include{Appendix/javadoc/com.kpro.algorithmbitmapDistanceWisOne}
\include{Appendix/javadoc/com.kpro.algorithmbitmapDistance}
\include{Appendix/javadoc/com.kpro.algorithmConclusionAlgorithm}
\include{Appendix/javadoc/com.kpro.algorithmConclusion-Simple}
\include{Appendix/javadoc/com.kpro.algorithmLearnAlgorithm}
\include{Appendix/javadoc/com.kpro.algorithmLearn-Constant}
\include{Appendix/javadoc/com.kpro.algorithmLearnAlgBasic}
\include{Appendix/javadoc/com.kpro.algorithmLearnAlgStand}

\section{Datastorage}
\include{Appendix/javadoc/com.kpro.datastoragePolicyDatabase}
\include{Appendix/javadoc/com.kpro.datastoragePDatabase}
\include{Appendix/javadoc/com.kpro.datastorageNRCouchdb}
\include{Appendix/javadoc/com.kpro.datastorageNetworkR}

\section{Dataobjects}
\include{Appendix/javadoc/com.kpro.dataobjectsPolicyObject}
\include{Appendix/javadoc/com.kpro.dataobjectsContext}
\include{Appendix/javadoc/com.kpro.dataobjectsAction}
\include{Appendix/javadoc/com.kpro.dataobjectsCase}
\include{Appendix/javadoc/com.kpro.dataobjectsRetention}
\include{Appendix/javadoc/com.kpro.dataobjectsRecipient}
\include{Appendix/javadoc/com.kpro.dataobjectsPurpose}
\include{Appendix/javadoc/com.kpro.dataobjectsCategory}

\section{Parser}
\include{Appendix/javadoc/com.kpro.parserP3PParser}

\section{UI}
\include{Appendix/javadoc/com.kpro.uiPrivacyAdvisorGUI}
\include{Appendix/javadoc/com.kpro.uiUserIO}
\include{Appendix/javadoc/com.kpro.uiUserIO-Simple}
\include{Appendix/javadoc/com.kpro.uiIO-Listing}

\section{Test}
\include{Appendix/javadoc/com.kpro.testrestReduction-KNN}
\include{Appendix/javadoc/com.kpro.testtestConclusion-Simple}
\include{Appendix/javadoc/com.kpro.testtestBitmap}
\include{Appendix/javadoc/com.kpro.testLearnAlgSimplerTest}

\section{Sample}
\include{Appendix/javadoc/com.kpro.sampleTemplateClass}
\include{Appendix/javadoc/com.kpro.sampleSerializationDemo}
\include{Appendix/javadoc/com.kpro.samplereadWeightConfig}
\include{Appendix/javadoc/com.kpro.samplemsgBox}
\include{Appendix/javadoc/com.kpro.samplejlistest}
\include{Appendix/javadoc/com.kpro.samplejfilechoosertest}
\include{Appendix/javadoc/com.kpro.sampleGioTest}
\include{Appendix/javadoc/com.kpro.sampledummy}
\include{Appendix/javadoc/com.kpro.sampledistanceMetricTest}
\include{Appendix/javadoc/com.kpro.sampleDeserializationDemo}

\@openrighttrue\makeatother

\include{Appendix/References}

\bibliographystyle{plain-annote}
\bibliography{mybibliography}


\printindex

\end{document}
\end

