\begin{jdclass}[class]{Gio}
\begin{jdclassheader}

\jdpublic 
\jdpackage{com.kpro.main}
\jdinherits{\jdtypesimple{Object}}
\end{jdclassheader}
\begin{jdinheritancetable} \jdInhEntry{\jdtypesimple{Object} clone(  )}{Object}
 \jdInhEntry{\jdtypesimple{boolean} equals( \jdtypesimple{Object} )}{Object}
 \jdInhEntry{\jdtypesimple{void} finalize(  )}{Object}
 \jdInhEntry{\jdtypesimple{Class} getClass(  )}{Object}
 \jdInhEntry{\jdtypesimple{int} hashCode(  )}{Object}
 \jdInhEntry{\jdtypesimple{void} notify(  )}{Object}
 \jdInhEntry{\jdtypesimple{void} notifyAll(  )}{Object}
 \jdInhEntry{\jdtypesimple{String} toString(  )}{Object}
 \jdInhEntry{\jdtypesimple{void} wait( \jdtypesimple{long} )}{Object}
 \jdInhEntry{\jdtypesimple{void} wait( \jdtypesimple{long}, \jdtypesimple{int} )}{Object}
 \jdInhEntry{\jdtypesimple{void} wait(  )}{Object}
\end{jdinheritancetable}
\begin{jdconstructor}
\jdpublic 
\JDpara{\jdtypearray{String}{\lbrack{}\rbrack{}}}{args}{}
\JDthrows{Exception}{Mostly from loadWeights, but should also happen for loadFromConfig}
\JDtext{Constructor fo gio class. There should only be one. Consider this a singleton instance to call I/O messages on.
 Constructs and parses command line arguements as well.}
\end{jdconstructor}
\begin{jdconstructor}
\jdpublic 
\JDpara{\jdtypearray{String}{\lbrack{}\rbrack{}}}{args}{any commandline arguements}
\JDpara{\jdtypesimple{UserIO}}{ui}{the known UserIO object}
\JDthrows{Exception}{Mostly from loadWeights, but should also happen for loadFromConfig}
\JDtext{A constructor permitting a user interface class to launch everything and be in control.}
\end{jdconstructor}
\begin{jdmethod}{configUI}
\jdpublic 
\jdtype{\jdtypesimple{void}}
\JDtext{call the user interface's general configuration method if the userInit option is true, and a user interface exists}
\end{jdmethod}
\begin{jdmethod}{setGenProps}
\jdpublic 
\jdtype{\jdtypesimple{void}}
\JDpara{\jdtypesimple{Properties}}{genProps}{}
\end{jdmethod}
\begin{jdmethod}{loadFromConfig}
\jdpublic 
\jdtype{\jdtypesimple{Properties}}
\JDpara{\jdtypesimple{String}}{fileLoc}{}
\JDtext{Loads the general configuration file, either from provided string, or default location (./PrivacyAdviser.cfg)}
\JDreturn{properties object corresponding to given configuration file}
\end{jdmethod}
\begin{jdmethod}{loadWeights}
\jdpublic 
\jdtype{\jdtypesimple{Properties}}
\JDthrows{Exception}{if there's an issue reading the file (if it doesn't exist, or has an IO error)}
\JDtext{Loads the weights configuration file, from the provided location}
\JDreturn{properties object corresponding to given configuration file}
\end{jdmethod}
\begin{jdmethod}{startLogger}
\jdpublic 
\jdtype{\jdtypesimple{Logger}}
\JDpara{\jdtypesimple{String}}{logLoc}{location of the output log file- a string}
\JDpara{\jdtypesimple{String}}{logLevel}{logging level (is parsed by level.parse())}
\JDtext{startLogger initializes and returns a file at logLoc with the results of logging at level logLevel.}
\JDreturn{Logger object to log to.}
\end{jdmethod}
\begin{jdmethod}{loadDB}
\jdpublic 
\jdtype{\jdtypesimple{void}}
\JDtext{Loads the case history into cache. 
 This is where the background database chosen.}
\end{jdmethod}
\begin{jdmethod}{getPDB}
\jdpublic 
\jdtype{\jdtypesimple{PolicyDatabase}}
\JDtext{returns the only policy database}
\JDreturn{the policy database}
\end{jdmethod}
\begin{jdmethod}{shutdown}
\jdpublic 
\jdtype{\jdtypesimple{void}}
\JDtext{closes resources and write everything to file}
\end{jdmethod}
\begin{jdmethod}{userResponse}
\jdpublic 
\jdtype{\jdtypesimple{PolicyObject}}
\JDpara{\jdtypesimple{PolicyObject}}{n}{the processed policy object}
\JDtext{Generates handles response. This is were we would pass stuff to cli or gui, etc}
\JDreturn{the policyObjected as accepted by user (potentially modified}
\end{jdmethod}
\begin{jdmethod}{loadPO}
\jdpublic 
\jdtype{\jdtypesimple{void}}
\JDtext{returns the policy object from the policyObject option}
\JDreturn{the policy object to be processed}
\end{jdmethod}
\begin{jdmethod}{getPO}
\jdpublic 
\jdtype{\jdtypesimple{PolicyObject}}
\end{jdmethod}
\begin{jdmethod}{isBuilding}
\jdpublic 
\jdtype{\jdtypesimple{boolean}}
\JDtext{returns the true if it should only build}
\JDreturn{true if a CBR should NOT be run}
\end{jdmethod}
\begin{jdmethod}{setWeights}
\jdpublic 
\jdtype{\jdtypesimple{void}}
\JDpara{\jdtypesimple{Properties}}{newWeightP}{the new weights file to save}
\JDtext{saves the new weights to a buffer variable before writing in the shutdown call}
\end{jdmethod}
\begin{jdmethod}{getCBR}
\jdpublic 
\jdtype{\jdtypesimple{CBR}}
\JDthrows{Exception}{}
\JDtext{returns the CBR to use}
\JDreturn{the cbr to use}
\end{jdmethod}
\begin{jdmethod}{getWeights}
\jdpublic 
\jdtype{\jdtypesimple{Properties}}
\JDtext{returns the originally imported set of weights}
\JDreturn{the weights for policy attributes}
\end{jdmethod}
\begin{jdmethod}{showDatabase}
\jdpublic 
\jdtype{\jdtypesimple{void}}
\JDtext{shows the database on the user interface, if the user interface exists and no user response is specied 
 and there is no 'blanketAccept' option.}
\end{jdmethod}
\begin{jdmethod}{fileExists}
\jdpublic 
\jdtype{\jdtypesimple{boolean}}
\JDpara{\jdtypesimple{String}}{filepath}{path of the file to check}
\JDtext{GUI classes should use this to ensure the user passes valid files to load.}
\JDreturn{true if the file exists, else false}
\end{jdmethod}
\begin{jdmethod}{getNR}
\jdpublic 
\jdtype{\jdtypesimple{NetworkR}}
\end{jdmethod}
\begin{jdmethod}{getConfLevel}
\jdpublic 
\jdtype{\jdtypesimple{double}}
\JDtext{gets the confidence level threshold from the configuration}
\JDreturn{the confidence threshold}
\end{jdmethod}
\end{jdclass}
