\begin{jdclass}[class]{NetworkR}
\begin{jdclassheader}

\jdabstract \jdpublic 
\jdpackage{com.kpro.datastorage}
\jdinherits{\jdtypesimple{Object}}
\JDtext{Network resources class. Abstract. See javadocs for what contains what. Should allow request for an action 
 (if local knowledge is insufficient), as well as saving to the community database.}
\JDauthor{ngerstle}
\JDversion{17.10.11.1}
\end{jdclassheader}
\begin{jdinheritancetable} \jdInhEntry{\jdtypesimple{Object} clone(  )}{Object}
 \jdInhEntry{\jdtypesimple{boolean} equals( \jdtypesimple{Object} )}{Object}
 \jdInhEntry{\jdtypesimple{void} finalize(  )}{Object}
 \jdInhEntry{\jdtypesimple{Class} getClass(  )}{Object}
 \jdInhEntry{\jdtypesimple{int} hashCode(  )}{Object}
 \jdInhEntry{\jdtypesimple{void} notify(  )}{Object}
 \jdInhEntry{\jdtypesimple{void} notifyAll(  )}{Object}
 \jdInhEntry{\jdtypesimple{String} toString(  )}{Object}
 \jdInhEntry{\jdtypesimple{void} wait( \jdtypesimple{long} )}{Object}
 \jdInhEntry{\jdtypesimple{void} wait( \jdtypesimple{long}, \jdtypesimple{int} )}{Object}
 \jdInhEntry{\jdtypesimple{void} wait(  )}{Object}
\end{jdinheritancetable}
\begin{jdconstructor}
\jdpublic 
\JDpara{\jdtypesimple{String}}{options}{}
\JDtext{Constructor- should accept as minimum the location of the networked database.}
\end{jdconstructor}
\begin{jdmethod}{reqAct}
\jdpublic \jdabstract 
\jdtype{\jdtypesimple{Action}}
\JDpara{\jdtypesimple{PolicyObject}}{a}{the PolicyObject to obtain a response for.}
\JDtext{accepts a PolicyObject, and returns the remote suggested action for it (the suggestion from the server).}
\JDreturn{the action to give the policy object.}
\end{jdmethod}
\begin{jdmethod}{saveObj}
\jdpublic \jdabstract 
\jdtype{\jdtypesimple{void}}
\JDpara{\jdtypesimple{PolicyObject}}{a}{the policy to upload remotely.}
\JDtext{sends a PolicyObject to the server. It needs to have complete Action attached.}
\end{jdmethod}
\begin{jdmethod}{disconnect}
\jdpublic \jdabstract 
\jdtype{\jdtypesimple{void}}
\JDtext{closes whatever resources were opened during initialization by the constructor}
\end{jdmethod}
\begin{jdmethod}{getInfo}
\jdpublic 
\jdtype{\jdtypesimple{String}}
\JDtext{returns the server type and location.}
\JDreturn{String "A "+ typeOfServer + " database located at "+ locationOfServer}
\end{jdmethod}
\end{jdclass}
