\begin{jdclass}[class]{PolicyDatabase}
\begin{jdclassheader}

\jdabstract \jdpublic 
\jdpackage{com.kpro.datastorage}
\jdimplements{Iterable}
\jdinherits{\jdtypesimple{Object}}
\JDtext{This is abstract class for databases. All policy 
 databases must implement this interface. Auto-generated
 via eclipse from PDatabase.java, then made abstract.
 Does enforce singleton-ness here. need to do it in each subclass.}
\JDauthor{ngerstle}
\JDversion{29.09.11.1}
\end{jdclassheader}
\begin{jdinheritancetable} \jdInhEntry{\jdtypesimple{Object} clone(  )}{Object}
 \jdInhEntry{\jdtypesimple{boolean} equals( \jdtypesimple{Object} )}{Object}
 \jdInhEntry{\jdtypesimple{void} finalize(  )}{Object}
 \jdInhEntry{\jdtypesimple{Class} getClass(  )}{Object}
 \jdInhEntry{\jdtypesimple{int} hashCode(  )}{Object}
 \jdInhEntry{\jdtypesimple{void} notify(  )}{Object}
 \jdInhEntry{\jdtypesimple{void} notifyAll(  )}{Object}
 \jdInhEntry{\jdtypesimple{String} toString(  )}{Object}
 \jdInhEntry{\jdtypesimple{void} wait( \jdtypesimple{long} )}{Object}
 \jdInhEntry{\jdtypesimple{void} wait( \jdtypesimple{long}, \jdtypesimple{int} )}{Object}
 \jdInhEntry{\jdtypesimple{void} wait(  )}{Object}
\end{jdinheritancetable}
\begin{jdmethod}{loadDB}
\jdpublic 
\jdtype{\jdtypesimple{void}}
\JDtext{Loads database from a file dLoc}
\JDauthor{ngerstle}
\end{jdmethod}
\begin{jdmethod}{loadDB}
\jdpublic \jdabstract 
\jdtype{\jdtypesimple{void}}
\JDpara{\jdtypesimple{String}}{dLoc}{the inlocation of the database file on disk}
\JDtext{Loads database from a file dLoc
 we have this public just in case we want to be able to load
 a db from a file other than where we plan to store it.}
\JDauthor{ngerstle}
\end{jdmethod}
\begin{jdmethod}{addPolicy}
\jdpublic 
\jdtype{\jdtypesimple{void}}
\JDpara{\jdtypesimple{PolicyObject}}{n}{the policy to add to the database}
\JDtext{Adds a PolicyObject to the database}
\end{jdmethod}
\begin{jdmethod}{iterator}
\jdpublic 
\jdtype{\jdtypesimple{Iterator}}
\JDtext{provides an iterator over the database's PolicyObjects}
\JDreturn{an iterator over the internal collection}
\end{jdmethod}
\begin{jdmethod}{closeDB}
\jdpublic 
\jdtype{\jdtypesimple{void}}
\JDtext{calls closeDB(PolicyDatabase.outlocation).
 needed due to lack of a good destructor system, as far as java goes (according to google)}
\end{jdmethod}
\begin{jdmethod}{closeDB}
\jdpublic \jdabstract 
\jdtype{\jdtypesimple{void}}
\JDpara{\jdtypesimple{String}}{dLoc}{the inlocation to save the data}
\JDtext{should implement writing the information contained by the PolicyDatabase to a file/disk}
\JDauthor{ngerstle}
\end{jdmethod}
\begin{jdmethod}{getDomain}
\jdpublic \jdabstract 
\jdtype{\jdtypesimple{ArrayList}}
\JDpara{\jdtypesimple{String}}{domain}{the domain to look for}
\JDtext{This class should return all policys for the given domain.}
\JDauthor{ngerstle}
\end{jdmethod}
\begin{jdmethod}{toString}
\jdpublic 
\jdtype{\jdtypesimple{String}}
\JDtext{Standard toString method}
\JDauthor{ulfnore}
\end{jdmethod}
\end{jdclass}
